---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
  [![Travis build status](https://travis-ci.org/fweber144/shinybrms.svg?branch=master)](https://travis-ci.org/fweber144/shinybrms)
<!-- badges: end -->

# Description

This [R](https://www.R-project.org/) package **shinybrms** provides a graphical user interface (GUI) for the R package [**brms**](https://CRAN.R-project.org/package=brms) which allows to fit Bayesian regression models using [Stan](https://mc-stan.org/) (more specifically, using its R interface, the R package [**rstan**](https://CRAN.R-project.org/package=rstan)). The GUI is a [Shiny](https://shiny.rstudio.com/) app, i.e. it was created using the R package [**shiny**](https://CRAN.R-project.org/package=shiny).

# Installation / Usage

There are two options for running the **shinybrms** Shiny app:

* Run the **shinybrms** Shiny app directly [from GitHub](https://github.com/fweber144/shinybrms/tree/master/inst/shinybrms_app).
* Install the R package **shinybrms** (either  [from GitHub](https://github.com/fweber144/shinybrms) or [from CRAN](https://CRAN.R-project.org/package=shinybrms)) and then run the **shinybrms** Shiny app from the installed package.

The first option is described in the following section "Without installation of 'shinybrms'". The second option is described in the subsequent section "With installation of 'shinybrms'". In both cases, you need to perform the following steps first:

1. Install R (see the [R homepage](https://www.R-project.org/)).
2. Install the R package **rstan** (see [this GitHub page](https://github.com/stan-dev/rstan/wiki/RStan-Getting-Started) for instructions).

## Without installation of 'shinybrms'

1. Install the R packages **brms** and **shiny**. You may use the following R code for this:
```{r, eval = FALSE}
install.packages(c("brms", "shiny"))
```
2. For full functionality of **shinybrms** (if desired), install the R packages **shinystan**, **callr**, **rstanarm**, and **lasso2**. You may use the following R code for this:
```{r, eval = FALSE}
install.packages(c("shinystan", "callr", "rstanarm", "lasso2"))
```
3. Launch the **shinybrms** Shiny app directly from GitHub by running the following R code:
```{r, eval = FALSE}
shiny::runGitHub("fweber144/shinybrms",
                 subdir = "inst/shinybrms_app",
                 launch.browser = TRUE)
```

## With installation of 'shinybrms'

1. Install the R package **shinybrms** either from GitHub or from CRAN. Note that installing from GitHub might give a more recent version of **shinybrms** than installing from CRAN. The R code for these two options is as follows:
    * To install **shinybrms** from GitHub:
    ```{r, eval = FALSE}
    if(!requireNamespace("devtools", quietly = TRUE)){
      install.packages("devtools")
    }
    devtools::install_github("fweber144/shinybrms")
    ```
    * To install **shinybrms** from CRAN:
    ```{r, eval = FALSE}
    install.packages("shinybrms")
    ```
2. Launch the **shinybrms** Shiny app by running the following R code:
```{r example, eval = FALSE}
library(shinybrms)
launch_shinybrms()
```
