---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
  [![Travis build status](https://travis-ci.org/fweber144/shinybrms.svg?branch=master)](https://travis-ci.org/fweber144/shinybrms)
<!-- badges: end -->

# Description

This [R](https://www.R-project.org/) package **shinybrms** provides a graphical user interface (GUI) for the R package [**brms**](https://CRAN.R-project.org/package=brms) which allows to fit Bayesian regression models using [Stan](https://mc-stan.org/) (more specifically, using its R interface, the R package [**rstan**](https://CRAN.R-project.org/package=rstan)). The GUI is a [Shiny](https://shiny.rstudio.com/) app, i.e. it was created using the R package [**shiny**](https://CRAN.R-project.org/package=shiny).

# Installation / Usage

There are two options for running the **shinybrms** Shiny app:

* Install the R package **shinybrms** (either  [from GitHub](https://github.com/fweber144/shinybrms) or [from CRAN](https://CRAN.R-project.org/package=shinybrms)) and then run the **shinybrms** Shiny app from the installed package.
* Run the **shinybrms** Shiny app directly [from GitHub](https://github.com/fweber144/shinybrms/tree/master/inst/shinybrms_app).

The first option is described in the following section "With installation of 'shinybrms'". The second option is described in the subsequent section "Without installation of 'shinybrms'". In both cases, you need to perform the following steps first:

1. Install R (see the [R homepage](https://www.R-project.org/)).
2. Install the R package **rstan** (see the ["RStan Getting Started" GitHub page](https://github.com/stan-dev/rstan/wiki/RStan-Getting-Started) for instructions; make sure to use `install.packages("rstan", [...], dependencies = TRUE)` with `[...]` as advised on the "RStan Getting Started" GitHub page).

## With installation of 'shinybrms'

1. Install the R package **shinybrms** either from GitHub or from CRAN. Note that installing from GitHub might give a more recent version of **shinybrms** than installing from CRAN. You also need to decide whether you want to use the example datasets from the R packages [**lme4**](https://CRAN.R-project.org/package=lme4), [**MASS**](https://CRAN.R-project.org/package=MASS), and [**rstanarm**](https://CRAN.R-project.org/package=rstanarm) or not.
    + If you *don't want* to use the example datasets from the R packages **lme4**, **MASS**, and **rstanarm**, then the R code for installing **shinybrms** from GitHub and CRAN (respectively) is as follows:
      * To install **shinybrms** from GitHub:
        ```{r, eval = FALSE}
        if(!requireNamespace("devtools", quietly = TRUE)){
          install.packages("devtools")
        }
        devtools::install_github("fweber144/shinybrms")
        ```
      * To install **shinybrms** from CRAN:
        ```{r, eval = FALSE}
        install.packages("shinybrms")
        ```
    + If you *want* to use the example datasets from the R packages **lme4**, **MASS**, and **rstanarm**, then the R code for installing **shinybrms** from GitHub and CRAN (respectively) is as follows:
      * To install **shinybrms** from GitHub:
        ```{r, eval = FALSE}
        if(!requireNamespace("devtools", quietly = TRUE)){
          install.packages("devtools")
        }
        devtools::install_github("fweber144/shinybrms", dependencies = TRUE)
        ```
      * To install **shinybrms** from CRAN:
        ```{r, eval = FALSE}
        install.packages("shinybrms", dependencies = TRUE)
        ```
2. Launch the **shinybrms** Shiny app by running the following R code:
  ```{r, eval = FALSE}
  library(shinybrms)
  launch_shinybrms()
  ```
  If you are using RStudio and you don't want to use RStudio's mechanism for opening the **shinybrms** app, then run the following R code:
  ```{r, eval = FALSE}
  library(shinybrms)
  launch_shinybrms(launch.browser = TRUE)
  ```

## Without installation of 'shinybrms'

1. Install the R package **brms**. You may use the following R code for this:
  ```{r, eval = FALSE}
  install.packages("brms")
  ```
2. If you want to use the example datasets from the R packages [**lme4**](https://CRAN.R-project.org/package=lme4), [**MASS**](https://CRAN.R-project.org/package=MASS), and [**rstanarm**](https://CRAN.R-project.org/package=rstanarm), you need to install these packages. You may use the following R code for this:
  ```{r, eval = FALSE}
  install.packages(c("lme4", "MASS", "rstanarm"))
  ```
3. Launch the **shinybrms** Shiny app directly from GitHub by running the following R code:
  ```{r, eval = FALSE}
  shiny::runGitHub("fweber144/shinybrms",
                   subdir = "inst/shinybrms_app")
  ```
  If you are using RStudio and you don't want to use RStudio's mechanism for opening the **shinybrms** app, then run the following R code:
  ```{r, eval = FALSE}
  shiny::runGitHub("fweber144/shinybrms",
                   subdir = "inst/shinybrms_app",
                   launch.browser = TRUE)
  ```
