---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<br>

<!-- badges: start -->
  [![Travis build status](https://travis-ci.org/fweber144/shinybrms.svg?branch=master)](https://travis-ci.org/fweber144/shinybrms)
<!-- badges: end -->

# **shinybrms** <img src='man/figures/logo.svg' align="right" height="139" />

<br>

## Description

The [R](https://www.R-project.org/) package [**shinybrms**](https://fweber144.github.io/shinybrms/) provides a graphical user interface (GUI) for fitting Bayesian regression models using the R package [**brms**](https://paul-buerkner.github.io/brms/) which in turn relies on [Stan](https://mc-stan.org/). The **shinybrms** GUI is a [Shiny](https://shiny.rstudio.com/) app.

To get an impression of the **shinybrms** app, have a look at [this page](https://fweber144.github.io/shinybrms/articles/shinybrms.html). The following text explains how to launch the **shinybrms** app.

## Launching the **shinybrms** app

There are two options for launching the **shinybrms** app:

* Install the R package **shinybrms** (either [from CRAN](https://CRAN.R-project.org/package=shinybrms) or [from GitHub](https://github.com/fweber144/shinybrms)) and then launch the **shinybrms** app from the installed package.
* Launch the **shinybrms** app directly [from GitHub](https://github.com/fweber144/shinybrms/tree/master/inst/shinybrms_app).

The first option is described in the following section "*With* installation of **shinybrms**". The second option is described in the subsequent section "*Without* installation of **shinybrms**". In both cases, you need to perform the following steps first:

1. Install R (see the [R homepage](https://www.R-project.org/)).
2. Install the R package [**rstan**](https://mc-stan.org/rstan/) (see the ["RStan Getting Started" GitHub page](https://github.com/stan-dev/rstan/wiki/RStan-Getting-Started) for instructions; make sure to use `install.packages("rstan", [...], dependencies = TRUE)` with `[...]` as advised on the "RStan Getting Started" GitHub page).

### *With* installation of **shinybrms**

1. Install the R package **shinybrms** either from CRAN or from GitHub. The GitHub version might be more recent than the CRAN version. You also need to decide whether you want to use the example datasets from the R packages [**lme4**](https://CRAN.R-project.org/package=lme4), [**MASS**](https://CRAN.R-project.org/package=MASS), and [**rstanarm**](https://mc-stan.org/rstanarm/) or not.
    + If you *don't want* to use the example datasets from the R packages **lme4**, **MASS**, and **rstanarm**, then the R code for installing **shinybrms** from CRAN and GitHub (respectively) is as follows:
      * To install **shinybrms** from CRAN:
        ```{r, eval = FALSE}
        install.packages("shinybrms")
        ```
      * To install **shinybrms** from GitHub:
        ```{r, eval = FALSE}
        if(!requireNamespace("devtools", quietly = TRUE)){
          install.packages("devtools")
        }
        devtools::install_github("fweber144/shinybrms")
        ```
    + If you *want* to use the example datasets from the R packages **lme4**, **MASS**, and **rstanarm**, then the R code for installing **shinybrms** from CRAN and GitHub (respectively) is as follows:
      * To install **shinybrms** from CRAN:
        ```{r, eval = FALSE}
        install.packages("shinybrms", dependencies = TRUE)
        ```
      * To install **shinybrms** from GitHub:
        ```{r, eval = FALSE}
        if(!requireNamespace("devtools", quietly = TRUE)){
          install.packages("devtools")
        }
        devtools::install_github("fweber144/shinybrms", dependencies = TRUE)
        ```
1. Launch the **shinybrms** app by either running the following R code:
   ```{r, eval = FALSE}
   library(shinybrms)
   launch_shinybrms()
   ```
   or this R code which ensures that the app opens up in the default web browser (helpful e.g. if you are using [RStudio](https://rstudio.com/)):
   ```{r, eval = FALSE}
   library(shinybrms)
   launch_shinybrms(launch.browser = TRUE)
   ```

### *Without* installation of **shinybrms**

1. Install the R package **brms**. You may use the following R code for this:
   ```{r, eval = FALSE}
   install.packages("brms")
   ```
1. If you want to use the example datasets from the R packages [**lme4**](https://CRAN.R-project.org/package=lme4), [**MASS**](https://CRAN.R-project.org/package=MASS), and [**rstanarm**](https://mc-stan.org/rstanarm/), you need to install these packages. You may use the following R code for this:
   ```{r, eval = FALSE}
   install.packages(c("lme4", "MASS", "rstanarm"))
   ```
1. Launch the **shinybrms** app directly from GitHub by either running the following R code:
   ```{r, eval = FALSE}
   shiny::runGitHub("fweber144/shinybrms",
                    subdir = "inst/shinybrms_app")
   ```
   or this R code which ensures that the app opens up in the default web browser (helpful e.g. if you are using [RStudio](https://rstudio.com/)):
   ```{r, eval = FALSE}
   shiny::runGitHub("fweber144/shinybrms",
                    subdir = "inst/shinybrms_app",
                    launch.browser = TRUE)
   ```
