---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
  [![Travis build status](https://travis-ci.org/fweber144/shinybrms.svg?branch=master)](https://travis-ci.org/fweber144/shinybrms)
<!-- badges: end -->

# Description

This [R](https://www.r-project.org/) package **shinybrms** provides a graphical user interface (GUI) for the R package [**brms**](https://CRAN.R-project.org/package=brms) which allows to fit Bayesian regression models using [Stan](https://mc-stan.org/) (more specifically, using its R interface, the R package [**rstan**](https://CRAN.R-project.org/package=rstan)). The GUI is a [Shiny](https://shiny.rstudio.com/) app, i.e. it was created using the R package [**shiny**](https://CRAN.R-project.org/package=shiny).

# Installation

If not already done, you need to install R first (see the [R homepage](https://www.r-project.org/)). Then, in R, perform the following steps:

1. Install the package [**rstan**](https://CRAN.R-project.org/package=rstan) (see [this GitHub page](https://github.com/stan-dev/rstan/wiki/RStan-Getting-Started) for instructions).
2. Install the package **shinybrms** with the following commands:
```{r, eval = FALSE}
if(!requireNamespace("devtools", quietly = TRUE)){
  install.packages("devtools")
}
devtools::install_github("fweber144/shinybrms")
```

# Usage

In R, launch the **shinybrms** Shiny app by typing:

```{r example, eval = FALSE}
library(shinybrms)
launch_shinybrms()
```
